Radio Properties of Young Protostars in the Central Filament of the Serpens South Infrared Dark Cloud

### 2014-12-24 Paper/paper.tex
modified:   Make_Figs.py 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib

@@

\subsection{Sources of Outflow}
\label{sec:outflows}
Radio continuum images have shown elongation with respect to radio jets etc etc...

@@

@@

-- Are the images to a high enough sensitivity to which I can say they are ``deep'' ? \\

>>>>

\begin{figure*}
\label{fig:vla4}
\centering
\includegraphics[keepaspectratio=True,scale=.7]{figures/SerpSouth_VLA4_contour.eps}
\caption{\small{ 
}}
\end{figure*}

@@

\subsection{Sources of Outflow}
\label{sec:outflows}
Early radio studies found that radio jet candidates are elongated in approximately the same direction as the large-scale outflow \citep{Anglada95}.

@@

-- Is it possible that VLA 2, 3 and 4 are all apart of a radio-loud extragalactic jet? \\

-- Given the size of the beam and the size of VLA 1 and 4, should they be considered ``resolved'' ? \\

@@

-- Are the images to a high enough sensitivity to which we can say they are ``deep'' ? \\

-- Title? \\
